Considering scale in multilayer animal social networks

### 2020-06-23 paper/manuscript.Rmd
prop locs

Increasing land cover resolution resulted in decreased availability of foraging habitat,
a rare habitat, and corresponding low connectivity of individuals in
these habitats at higher resolution (Figure \@ref(fig:lcres)). Edge overlap were relatively consistent across land cover resolutions for
forest and open layers (Figure \@ref(fig:lcres) D). Edge overlap decreased
sharply between 30 m and 600 m in foraging layers, afterwards remaining stable to
1000 m (Figure \@ref(fig:lcres) D). Graph strength was more variable within
foraging habitat layers across land cover resolutions than open and forest habitat layers (Figure
\@ref(fig:lcres) E). 
The proportion of relocations in forest and open habitats
increased with increasing spatial resolution, while decreasing in foraging habitat
(14.5% at 30 m - <2% at 1000 m).  Overall, these results indicate the importance of
matching land cover resolution to scale of selection as well as ensuring the
land cover product used has a resolution fine enough to detect landscape
features and habitats relevant to study species, such as important patchy and
rare habitats.

>>>>

Increasing land cover resolution resulted in decreased availability of foraging habitat and corresponding low connectivity of individuals at higher land cover resolutions. Edge overlap decreased
sharply between 30 m and 600 m in foraging layers, afterwards remaining stable to
1000 m (Figure \@ref(fig:lcres) D). In contrast, edge overlap was relatively consistent across land cover resolutions in
forest and open layers (Figure \@ref(fig:lcres) D).  Graph strength was more variable within
foraging habitat layers across land cover resolutions than open and forest habitat layers (Figure
\@ref(fig:lcres) E). 
The proportion of relocations in forest (42.1% at 30 m - 48.2% at 1000 m) and open (43.3% at 30 m - 50.3% at 1000 m) habitats
increased with increasing spatial resolution, while decreasing in foraging habitat
(14.5% at 30 m - <2% at 1000 m).  Overall, these results indicate the importance of
matching land cover resolution to scale of selection as well as ensuring the
land cover product used has a resolution fine enough to detect landscape
features and habitats relevant to study species, such as important patchy and
rare habitats.
